---
title: "Research Radar"
subtitle: "Hydrology, Open Data and Uncertainty"
format:
  html:
    toc: true
    toc-location: right
    page-layout: article
execute:
  warning: false
  message: false
  echo: false
---

```{=html}
<style>
body {
  background: #f7f6f2;
  color: #1f1f1c;
}

.quarto-title-banner {
  background: #f7f6f2;
  color: #1f1f1c;
  border-bottom: 1px solid #d8d5cc;
}

.quarto-title h1.title {
  font-weight: 750;
  letter-spacing: -0.03em;
}

.subtitle {
  color: #6f6b63;
}

.note-box {
  margin: 1.5rem 0 2rem 0;
  padding: 1rem 1.2rem;
  background: #eeece7;
  border: 1px solid #d8d5cc;
  border-radius: 12px;
  color: #5f5b54;
  font-size: 0.96rem;
  line-height: 1.55;
}

.article-grid {
  display: grid;
  grid-template-columns: 1fr;
  gap: 0.8rem;
  margin-top: 1rem;
}

.article-card {
  background: #fbfaf7;
  border: 1px solid #d8d5cc;
  border-left: 5px solid #2E86E8;
  border-radius: 12px;
  padding: 0.95rem 1.05rem;
}

.article-title {
  font-weight: 680;
  line-height: 1.38;
}

.article-code {
  display: inline-block;
  font-family: monospace;
  font-size: 0.78rem;
  font-weight: 750;
  color: white;
  background: #2E86E8;
  padding: 0.16rem 0.42rem;
  border-radius: 5px;
  margin-right: 0.45rem;
}

.article-meta {
  margin-top: 0.42rem;
  color: #6f6b63;
  font-size: 0.9rem;
}

.badge {
  display: inline-block;
  font-size: 0.74rem;
  font-weight: 700;
  padding: 0.12rem 0.45rem;
  border-radius: 999px;
  border: 1px solid #d8d5cc;
  background: #eeece7;
  color: #5f5b54;
  margin-right: 0.35rem;
}

.pillar-grid {
  display: grid;
  grid-template-columns: repeat(auto-fit, minmax(260px, 1fr));
  gap: 0.8rem;
  margin-top: 1rem;
}

.pillar-card {
  background: #fbfaf7;
  border: 1px solid #d8d5cc;
  border-radius: 12px;
  padding: 0.9rem 1rem;
}

.pillar-name {
  font-weight: 720;
  margin-bottom: 0.25rem;
}

.pillar-desc {
  color: #6f6b63;
  font-size: 0.92rem;
  line-height: 1.45;
}

.score-table {
  width: 100%;
  border-collapse: collapse;
  margin-top: 1rem;
  font-size: 0.88rem;
}

.score-table th {
  background: #eeece7;
  color: #1f1f1c;
  border: 1px solid #d8d5cc;
  padding: 0.45rem;
  text-align: center;
}

.score-table td {
  border: 1px solid #d8d5cc;
  padding: 0.45rem;
  text-align: center;
}

.score-table td:first-child {
  font-weight: 700;
  font-family: monospace;
}

a {
  color: #2E86E8;
}
</style>
```

```{r}
articles <- data.frame(
  code = paste0("A", 1:7),
  title = c(
    "Comparativa de modelos tradicionales vs machine learning para el relleno de datos faltantes en series de caudales diarios en cuencas representativas del Perú",
    "Corrección de sesgo y transferencia estadística en series de precipitación máxima anual satelital en el río Piura",
    "Bias-Corrected Precipitation Products in a Data-Scarce Andean Basin: Performance and Parameter Transferability",
    "Uncertainty in Indirect IDF Estimation Using Open Precipitation Datasets",
    "Structural limitations of precipitation-only streamflow modelling in Andean basins under ENSO-driven and glacier-influenced regimes",
    "Does daily performance guarantee annual reliability? Uncertainty propagation from gap-filled streamflow records into water balance estimation in data-scarce basins",
    "GLUE-Limits of Acceptability Framework for Rainfall-Runoff Simulation in an Ungauged Arid Catchment: Regional Constraints and Precipitation-Product Evaluation"
  ),
  status = c(
    "Published",
    "Published",
    "Manuscript",
    "Manuscript",
    "Manuscript",
    "Manuscript",
    "Manuscript"
  ),
  venue = c(
    "Tecnología y Ciencias del Agua",
    "Ingeniería del Agua",
    "RBRH - Revista Brasileira de Recursos Hídricos",
    "Revista Facultad de Ingeniería Universidad de Antioquia",
    "Hydrological Sciences Journal",
    "Water Resources Management",
    "Journal of Hydrologic Engineering"
  ),
  doi = c(
    "10.24850/j-tyca-18-02-02",
    "10.4995/ia.24476",
    "",
    "",
    "",
    "",
    ""
  ),
  stringsAsFactors = FALSE
)

pillars <- c(
  "Surface\nhydrology",
  "River\nhydraulics",
  "Hydrogeology",
  "Hydrometeorology",
  "Water\nquality",
  "Water\nmanagement",
  "Statistical\nhydrology",
  "Remote sensing /\nHydroinformatics"
)

pillar_names <- c(
  "Surface hydrology",
  "River hydraulics",
  "Hydrogeology",
  "Hydrometeorology",
  "Water quality",
  "Water management",
  "Statistical hydrology",
  "Remote sensing / Hydroinformatics"
)

pillar_desc <- c(
  "Rainfall-runoff processes, streamflow estimation, hydrological signatures, and catchment response.",
  "Channel flow, routing, hydraulic interpretation, and flood-related applications.",
  "Groundwater processes and aquifer-centered analysis.",
  "Precipitation, climate variability, satellite/reanalysis products, and extreme rainfall.",
  "Water chemistry, pollution, ecological indicators, and environmental water quality.",
  "Planning, water balance, decision support, infrastructure, and resource management implications.",
  "Uncertainty, bias correction, frequency analysis, gap filling, and statistical methods.",
  "Open datasets, reproducible coding, geospatial workflows, machine learning, and satellite products."
)

scores <- data.frame(
  surface_hydrology = c(9, 8, 6, 8, 9, 9, 10),
  river_hydraulics = c(1, 1, 1, 3, 2, 1, 2),
  hydrogeology = c(0, 0, 0, 0, 0, 0, 0),
  hydrometeorology = c(4, 9, 9, 9, 8, 3, 7),
  water_quality = c(0, 0, 0, 0, 0, 0, 0),
  water_management = c(5, 4, 5, 6, 5, 9, 6),
  statistical_hydrology = c(9, 8, 8, 9, 8, 9, 8),
  remote_sensing_hydroinformatics = c(8, 9, 9, 8, 9, 6, 8)
)

colnames(scores) <- pillars

colors <- c(
  "#2E86E8",
  "#1DAF8A",
  "#E85A30",
  "#9B59B6",
  "#E67E22",
  "#E91E8C",
  "#27AE60"
)
```

```{=html}
<div class="note-box">
This radar summarizes the thematic orientation of my research work. Scores do not represent article quality, journal rank, or scientific impact. They indicate the relative emphasis of each study across hydrological and methodological domains.
</div>
```

## Research profile

```{r}
#| fig-width: 9
#| fig-height: 6.6
#| fig-align: center
#| out-width: "95%"

library(fmsb)

fills <- adjustcolor(colors, alpha.f = 0.13)

radar_df <- rbind(
  rep(10, length(pillars)),
  rep(0, length(pillars)),
  scores
)

op <- par(
  bg = "#f7f6f2",
  mar = c(0.8, 0.8, 2.0, 0.8),
  family = "sans"
)

radarchart(
  radar_df,
  axistype = 1,
  pcol = colors,
  pfcol = fills,
  plwd = 2.2,
  plty = 1,
  cglcol = "#d8d5cc",
  cglty = 1,
  cglwd = 0.8,
  axislabcol = "#77736b",
  caxislabels = c("", "2", "4", "6", "8", "10"),
  calcex = 0.72,
  vlcex = 0.78,
  vlabels = pillars,
  title = "Research Radar - Hydrology, Open Data and Uncertainty"
)

legend(
  "bottomleft",
  legend = paste0(articles$code, "  ", articles$status),
  col = colors,
  lty = 1,
  lwd = 2.3,
  pch = 19,
  bty = "n",
  cex = 0.70,
  text.col = "#44413c",
  pt.cex = 0.8
)

par(op)
```

## Interpretation

My current research profile is concentrated in surface hydrology, hydrometeorology, statistical hydrology, uncertainty analysis, and hydroinformatics. This reflects a methodological focus on open hydroclimatic datasets, rainfall-runoff modelling, bias correction, gap filling, regional constraints, and reproducible workflows for data-scarce basins.

The radar also shows the boundaries of this research line. Hydrogeology, water quality, and hydroecology are not central components of the studies represented here. This is not a weakness of the individual papers, but a deliberate delimitation of the research program.

## Articles included

```{r}
#| results: asis

cat('<div class="article-grid">')

for (i in seq_len(nrow(articles))) {
  doi_text <- if (articles$doi[i] == "") {
    "DOI: -"
  } else {
    paste0(
      'DOI: <a href="https://doi.org/',
      articles$doi[i],
      '" target="_blank">',
      articles$doi[i],
      "</a>"
    )
  }

  cat(
    paste0(
      '<div class="article-card" style="border-left-color:', colors[i], ';">',
      '<div class="article-title">',
      '<span class="article-code" style="background:', colors[i], ';">', articles$code[i], '</span>',
      articles$title[i],
      '</div>',
      '<div class="article-meta">',
      '<span class="badge">', articles$status[i], '</span>',
      articles$venue[i],
      ' · ',
      doi_text,
      '</div>',
      '</div>'
    )
  )
}

cat('</div>')
```

## Thematic pillars

```{r}
#| results: asis

cat('<div class="pillar-grid">')

for (i in seq_along(pillar_names)) {
  cat(
    paste0(
      '<div class="pillar-card">',
      '<div class="pillar-name">', pillar_names[i], '</div>',
      '<div class="pillar-desc">', pillar_desc[i], '</div>',
      '</div>'
    )
  )
}

cat('</div>')
```

## Scoring logic

The thematic scores range from 0 to 10 and describe the relative emphasis of each article across the eight pillars. A high score means that the pillar is central to the article. A low score means that the pillar is peripheral or absent.

```{r}
#| results: asis

score_table <- data.frame(
  Code = articles$code,
  Surface = scores[[1]],
  River = scores[[2]],
  Hydrogeology = scores[[3]],
  Hydrometeorology = scores[[4]],
  Quality = scores[[5]],
  Management = scores[[6]],
  Statistics = scores[[7]],
  Hydroinformatics = scores[[8]]
)

cat('<table class="score-table">')
cat('<thead><tr>')

for (nm in names(score_table)) {
  cat(paste0('<th>', nm, '</th>'))
}

cat('</tr></thead>')
cat('<tbody>')

for (i in seq_len(nrow(score_table))) {
  cat('<tr>')
  for (j in seq_len(ncol(score_table))) {
    cat(paste0('<td>', score_table[i, j], '</td>'))
  }
  cat('</tr>')
}

cat('</tbody></table>')
```
